hatchR: A tool set to predict when fish hatch and emerge

### 2025-03-13 inst/poster/hatchR_posterdown/hatchR_posterdown.Rmd

---
title: "hatchR: A tool set to predict when fish hatch and emerge"
author:
  - name: Morgan Sparks
    affil: 1
  - name: Eli Felts
    affil: 2
  - name: Allison Swartz
    affil: 3
  - name: Bryan Maitland
    affil: 1
affiliation:
  - num: 1
    address: Rocky Mountain Research Station, US Forest Service
  - num: 2
    address: Idaho Fish and Wildlife Conservation Oﬀice, US Fish and Wildlife Service
  - num: 3
    address: College of Forestry, Oregon State University
column_numbers: 4
logoright_name: "./hatchR_posterdown_files/figure-html/agency_logos.png"
logoleft_name: "./hatchR_posterdown_files/figure-html/logo.png"
poster_height: "36in"
poster_width: "48in"
primary_colour: "	#011f4b"
sectitle_bgcol: "#005b96"
sectitle_bordercol: "#005b96"
column_margins: "0.33in"
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

@@

```{r, out.width='36%', fig.align='center', fig.cap= "hatchR workflow. Processes are presented as filled circles, functions as plain text rectangles, and decisions as italicized text."}

@@

```{r, out.width='75%', fig.align='center', fig.cap= "Predicted days to hatch using custom parameterizations for three warmwater species with mean 16 °C thermal regime."}
###  make temp regime
set.seed(123)
# create random temps and corresponding dates
temps_sim <- sort(rnorm(n =30, mean = 16, sd = 1), decreasing = FALSE)
dates_sim <-  seq(from = ymd("2000-07-01"),
             to = ymd("2000-07-31"), length.out = 30)

@@

Our model predicts Bull Trout will emerge 204 days after September 30th, which is April 22 or well before the July 1 date of road construction.

@@

```{r, fig.height = 8.75, fig.align='center', fig.cap= "Predicted hatch timing for 139 putatuve Bull Trout sites for three spawning periods."}
cut_ints <- date(
  c(
    "2011-08-31", "2012-08-31",
    "2013-08-31", "2014-08-31",
    "2015-08-31"
  )
)

>>>>

---
title: "hatchR: A tool set to predict when fish hatch and emerge"
author:
  - name: Morgan Sparks
    affil: 1
  - name: Eli Felts
    affil: 2
  - name: Allison Swartz
    affil: 3
  - name: Bryan Maitland
    affil: 1
affiliation:
  - num: 1
    address: Rocky Mountain Research Station, US Forest Service
  - num: 2
    address: Idaho Fish and Wildlife Conservation Oﬀice, US Fish and Wildlife Service
  - num: 3
    address: College of Forestry, Oregon State University
column_numbers: 4
logoright_name: "./hatchR_posterdown_files/figure-html/agency_logos.png"
logoleft_name: "./hatchR_posterdown_files/figure-html/logo.png"
poster_height: "36in"
poster_width: "48in"
primary_colour: "#011f4b"
secondary_colour: "#011f4b"
author_textcol: "white"
titlebox_borderwidth: "1cm"
titlebox_bordercol: "#011f4b"
sectitle_bgcol: "#005b96"
sectitle_bordercol: "#005b96"
column_margins: "0.33in"
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

@@

```{r, out.width='34%', fig.align='center', fig.cap= "hatchR workflow. Processes are presented as filled circles, functions as plain text rectangles, and decisions as italicized text."}

@@

```{r, out.width='73%', fig.align='center', fig.cap= "Predicted days to hatch using custom parameterizations for three warmwater species with mean 16 °C thermal regime."}
###  make temp regime
set.seed(123)
# create random temps and corresponding dates
temps_sim <- sort(rnorm(n =30, mean = 16, sd = 1), decreasing = FALSE)
dates_sim <-  seq(from = ymd("2000-07-01"),
             to = ymd("2000-07-31"), length.out = 30)

@@

Our model predicts Bull Trout will emerge 204 days after September 30, which is April 22 or well before the July 1 date of road construction.

@@

```{r, fig.height = 8.75, fig.align='center', fig.cap= "Predicted hatch timing for 139 putative Bull Trout sites for three spawning periods."}
cut_ints <- date(
  c(
    "2011-08-31", "2012-08-31",
    "2013-08-31", "2014-08-31",
    "2015-08-31"
  )
)
